\textsf{Are frontier models superhuman chemists?}

### 2024-03-12 src/tex/ms.tex
continue analysis leads

In \Cref{fig:estimated_difficulty} we show that there is no significant correlation between the estimated difficulty and whether the models answered the question correctly or not.
For applications in which humans might rely on the models to provide answers, this is a concerning observation highlighting the need for critical reasoning in the interpretation of the models' outputs.\cite{Li_2023}

>>>>

In \Cref{fig:estimated_difficulty} we show that there is no significant correlation between the estimated difficulty and whether the models answered the question correctly or not.
For applications in which humans might rely on the models to provide answers, this is a concerning observation highlighting the need for critical reasoning in the interpretation of the models' outputs.\cite{Li_2023}
For example, for the questions about the safety profile of compounds, GPT-4 reported an average confidence of XX (on a scale of 1--5) for the XX (out of XX) questions it answered in correctly (XX for the XX questions it answered correctly).
